{\bf {\Large Evaluation and correction of noise related to physical processes in estimates of estuary metabolism}}

### 2014-07-29 swmp_noise.Rnw
added data for case studies with multiple window combs, fixed tables, started some agg plots for metab

% example from SAPDC
\centering\vspace*{\fill}
<<case_ex1, cache = F, fig.height = 7.5, fig.width = 5.5, out.width = '0.8\\textwidth', eval = T, echo = F, fig.cap = 'Example of metabolism and \\ac{DO} time series before (observed) and after (detided) weighted regression. Results are for a ten day period in March for the Sapelo Island station.'>>=
######
# SAPDC example

load('met_ls_inst.RData')
load('met_ls.RData')

# subsets by case and date range
case <- 'SAPDC'
dat.rng<-as.Date(c('2012-03-20','2012-03-29'))

met_subs <- met_ls[[paste(case, 'wtreg.RData', sep = '_')]]
inst_subs <- met_ls_inst[[paste(case, 'wtreg.RData', sep = '_')]]

# subset data
met.rng <- met_subs$Date<=dat.rng[2] & met_subs$Date>=dat.rng[1]
met_subs <- met_subs[met.rng,]

inst_subs$Date <- as.Date(inst_subs$DateTimeStamp)
inst.rng <- inst_subs$Date<=dat.rng[2] & inst_subs$Date>=dat.rng[1]
inst_subs <- inst_subs[inst.rng,]

##
# custom theme, mod of theme_bw

my_theme <- theme(
  legend.title = element_blank(),legend.position = 'top',
  axis.title.x = element_blank(),legend.box= 'horizontal',
  plot.margin= unit(c(0, 1, 0, 1), "lines") # top right bottom left
  )

# function for setting range on y axis
rng.fun<-function(vec.in){
  rngs<-range(vec.in,na.rm=T)
  buffs<-0.07*abs(diff(rngs))
  c(rngs[1]-buffs,rngs[2]+buffs)
  }

##
# metab plot
to_plo1 <- melt(met_subs, id.var = c('Date'), 
  measure.var = grep('Pg|Rt|NEM', names(met_subs), value = T)
  )
to_plo1$Input <- 'Observed'
to_plo1$Input[grep('dtd', to_plo1$variable)] <- 'Detided'
to_plo1$Input <- factor(to_plo1$Input, levels = c('Observed', 'Detided'))
to_plo1$variable <- gsub('_dtd', '', to_plo1$variable)

ylab<-expression(paste('DO (g ',m^-2, d^-1, ')'))
p1 <- ggplot(to_plo1, aes(x = Date, y = 0.032 * value, group = variable,
    colour = variable)) +
  geom_line() +
  theme_bw() +
  geom_point(size = 2) +
  facet_wrap(~Input, ncol = 1) +
  scale_y_continuous(ylab)  +
  my_theme

##
# DO plot
to_plo2 <- met.day.fun(inst_subs, case)
names(to_plo2)[names(to_plo2) %in% 'variable'] <- 'solar'
ggpoly <- poly.fun(to_plo2$solar, to_plo2)

ylab<-expression(paste('DO (mg ',L^-1,')'))
p2 <- ggplot(to_plo2, aes(x = DateTimeStamp)) + 
  ggpoly +
  geom_line(aes(y = DO_obs, colour = 'Observed')) +
  geom_line(aes(y = DO_dtd, colour = 'Detided')) +
  coord_cartesian(ylim = c(0,9)) +
  scale_fill_manual(values='orange',labels='Day') +
  theme_bw() +
  scale_y_continuous(ylab)  +
  my_theme

## 
# tide plot
to_plo3 <- met.day.fun(inst_subs, case)
names(to_plo2)[names(to_plo2) %in% 'variable'] <- 'solar'
ggpoly <- poly.fun(to_plo2$solar, to_plo2)

ylab<-expression(paste('Height (m)'))
p3 <- ggplot(to_plo3, aes(x = DateTimeStamp)) + 
  ggpoly +
  geom_line(aes(y = Tide, colour = TotPAR)) +
  coord_cartesian(ylim = rng.fun(to_plo3$Tide)) +
  scale_fill_manual(values='orange',labels='Day') +
  theme_bw() +  
  my_theme + 
  scale_y_continuous(ylab) +
  scale_colour_gradient(low='blue', high='yellow',
    guide = guide_colorbar(direction = "horizontal",barheight= 0.3))

# Get the widths
pA <- ggplot_gtable(ggplot_build(p1))
pB <- ggplot_gtable(ggplot_build(p2))
pC <- ggplot_gtable(ggplot_build(p3))
maxWidth = unit.pmax(pA$widths[2:3], pB$widths[2:3], 
                     pC$widths[2:3])

# Set the widths
pA$widths[2:3] <- maxWidth
pB$widths[2:3] <- maxWidth
pC$widths[2:3] <- maxWidth

grid.arrange(pA, pB, pC, ncol = 1, heights = c(1.7, 1, 1))

% example from ELKVM
\centering\vspace*{\fill}
<<case_ex2, cache = F, fig.height = 7.5, fig.width = 5.5, out.width = '0.8\\textwidth', eval = T, echo = F, fig.cap = 'Example of metabolism and \\ac{DO} time series before (observed) and after (detided) weighted regression. Results are for a ten day period in March for the Elkhorn Slough station.'>>=
######
# ELKVM example

load('met_ls_inst.RData')
load('met_ls.RData')

# subsets by case and date range
case <- 'ELKVM'
dat.rng<-as.Date(c('2012-07-10','2012-07-20'))

met_subs <- met_ls[[paste(case, 'wtreg.RData', sep = '_')]]
inst_subs <- met_ls_inst[[paste(case, 'wtreg.RData', sep = '_')]]

# subset data
met.rng <- met_subs$Date<=dat.rng[2] & met_subs$Date>=dat.rng[1]
met_subs <- met_subs[met.rng,]

inst_subs$Date <- as.Date(inst_subs$DateTimeStamp)
inst.rng <- inst_subs$Date<=dat.rng[2] & inst_subs$Date>=dat.rng[1]
inst_subs <- inst_subs[inst.rng,]

##
# custom theme, mod of theme_bw

my_theme <- theme(
  legend.title = element_blank(),legend.position = 'top',
  axis.title.x = element_blank(),legend.box= 'horizontal',
  plot.margin= unit(c(0, 1, 0, 1), "lines") # top right bottom left
  )

# function for setting range on y axis
rng.fun<-function(vec.in){
  rngs<-range(vec.in,na.rm=T)
  buffs<-0.07*abs(diff(rngs))
  c(rngs[1]-buffs,rngs[2]+buffs)
  }

##
# metab plot
to_plo1 <- melt(met_subs, id.var = c('Date'), 
  measure.var = grep('Pg|Rt|NEM', names(met_subs), value = T)
  )
to_plo1$Input <- 'Observed'
to_plo1$Input[grep('dtd', to_plo1$variable)] <- 'Detided'
to_plo1$Input <- factor(to_plo1$Input, levels = c('Observed', 'Detided'))
to_plo1$variable <- gsub('_dtd', '', to_plo1$variable)

ylab<-expression(paste('DO (g ',m^-2, d^-1, ')'))
p1 <- ggplot(to_plo1, aes(x = Date, y = 0.032 * value, group = variable,
    colour = variable)) +
  geom_line() +
  theme_bw() +
  geom_point(size = 2) +
  facet_wrap(~Input, ncol = 1) +
  scale_y_continuous(ylab)  +
  my_theme

##
# DO plot
to_plo2 <- met.day.fun(inst_subs, case)
names(to_plo2)[names(to_plo2) %in% 'variable'] <- 'solar'
ggpoly <- poly.fun(to_plo2$solar, to_plo2)

ylab<-expression(paste('DO (mg ',L^-1,')'))
p2 <- ggplot(to_plo2, aes(x = DateTimeStamp)) + 
  ggpoly +
  geom_line(aes(y = DO_obs, colour = 'Observed')) +
  geom_line(aes(y = DO_dtd, colour = 'Detided')) +
  coord_cartesian(ylim = rng.fun(to_plo2$DO_obs)) +
  scale_fill_manual(values='orange',labels='Day') +
  theme_bw() +
  scale_y_continuous(ylab)  +
  my_theme

## 
# tide plot
to_plo3 <- met.day.fun(inst_subs, case)
names(to_plo2)[names(to_plo2) %in% 'variable'] <- 'solar'
ggpoly <- poly.fun(to_plo2$solar, to_plo2)

ylab<-expression(paste('Height (m)'))
p3 <- ggplot(to_plo3, aes(x = DateTimeStamp)) + 
  ggpoly +
  geom_line(aes(y = Tide, colour = TotPAR)) +
  coord_cartesian(ylim = rng.fun(to_plo3$Tide)) +
  scale_fill_manual(values='orange',labels='Day') +
  theme_bw() +  
  my_theme + 
  scale_y_continuous(ylab) +
  scale_colour_gradient(low='blue', high='yellow',
    guide = guide_colorbar(direction = "horizontal",barheight= 0.3))

# Get the widths
pA <- ggplot_gtable(ggplot_build(p1))
pB <- ggplot_gtable(ggplot_build(p2))
pC <- ggplot_gtable(ggplot_build(p3))
maxWidth = unit.pmax(pA$widths[2:3], pB$widths[2:3], 
                     pC$widths[2:3])

# Set the widths
pA$widths[2:3] <- maxWidth
pB$widths[2:3] <- maxWidth
pC$widths[2:3] <- maxWidth

grid.arrange(pA, pB, pC, ncol = 1, heights = c(1.7, 1, 1))

% example from pdbby
\centering\vspace*{\fill}
<<case_ex3, cache = F, fig.height = 7.5, fig.width = 5.5, out.width = '0.8\\textwidth', eval = T, echo = F, fig.cap = 'Example of metabolism and \\ac{DO} time series before (observed) and after (detided) weighted regression. Results are for a ten day period in March for the Padilla Bay station.'>>=
######
# PDBBY example

load('met_ls_inst.RData')
load('met_ls.RData')

# subsets by case and date range
case <- 'PDBBY'
dat.rng<-as.Date(c('2012-07-10','2012-07-20'))

met_subs <- met_ls[[paste(case, 'wtreg.RData', sep = '_')]]
inst_subs <- met_ls_inst[[paste(case, 'wtreg.RData', sep = '_')]]

# subset data
met.rng <- met_subs$Date<=dat.rng[2] & met_subs$Date>=dat.rng[1]
met_subs <- met_subs[met.rng,]

inst_subs$Date <- as.Date(inst_subs$DateTimeStamp)
inst.rng <- inst_subs$Date<=dat.rng[2] & inst_subs$Date>=dat.rng[1]
inst_subs <- inst_subs[inst.rng,]

##
# custom theme, mod of theme_bw

my_theme <- theme(
  legend.title = element_blank(),legend.position = 'top',
  axis.title.x = element_blank(),legend.box= 'horizontal',
  plot.margin= unit(c(0, 1, 0, 1), "lines") # top right bottom left
  )

# function for setting range on y axis
rng.fun<-function(vec.in){
  rngs<-range(vec.in,na.rm=T)
  buffs<-0.07*abs(diff(rngs))
  c(rngs[1]-buffs,rngs[2]+buffs)
  }

##
# metab plot
to_plo1 <- melt(met_subs, id.var = c('Date'), 
  measure.var = grep('Pg|Rt|NEM', names(met_subs), value = T)
  )
to_plo1$Input <- 'Observed'
to_plo1$Input[grep('dtd', to_plo1$variable)] <- 'Detided'
to_plo1$Input <- factor(to_plo1$Input, levels = c('Observed', 'Detided'))
to_plo1$variable <- gsub('_dtd', '', to_plo1$variable)

ylab<-expression(paste('DO (g ',m^-2, d^-1, ')'))
p1 <- ggplot(to_plo1, aes(x = Date, y = 0.032 * value, group = variable,
    colour = variable)) +
  geom_line() +
  theme_bw() +
  geom_point(size = 2) +
  facet_wrap(~Input, ncol = 1) +
  scale_y_continuous(ylab)  +
  my_theme

##
# DO plot
to_plo2 <- met.day.fun(inst_subs, case)
names(to_plo2)[names(to_plo2) %in% 'variable'] <- 'solar'
ggpoly <- poly.fun(to_plo2$solar, to_plo2)

ylab<-expression(paste('DO (mg ',L^-1,')'))
p2 <- ggplot(to_plo2, aes(x = DateTimeStamp)) + 
  ggpoly +
  geom_line(aes(y = DO_obs, colour = 'Observed')) +
  geom_line(aes(y = DO_dtd, colour = 'Detided')) +
  coord_cartesian(ylim = rng.fun(to_plo2$DO_obs)) +
  scale_fill_manual(values='orange',labels='Day') +
  theme_bw() +
  scale_y_continuous(ylab)  +
  my_theme

## 
# tide plot
to_plo3 <- met.day.fun(inst_subs, case)
names(to_plo2)[names(to_plo2) %in% 'variable'] <- 'solar'
ggpoly <- poly.fun(to_plo2$solar, to_plo2)

ylab<-expression(paste('Height (m)'))
p3 <- ggplot(to_plo3, aes(x = DateTimeStamp)) + 
  ggpoly +
  geom_line(aes(y = Tide, colour = TotPAR)) +
  coord_cartesian(ylim = rng.fun(to_plo3$Tide)) +
  scale_fill_manual(values='orange',labels='Day') +
  theme_bw() +  
  my_theme + 
  scale_y_continuous(ylab) +
  scale_colour_gradient(low='blue', high='yellow',
    guide = guide_colorbar(direction = "horizontal",barheight= 0.3))

# Get the widths
pA <- ggplot_gtable(ggplot_build(p1))
pB <- ggplot_gtable(ggplot_build(p2))
pC <- ggplot_gtable(ggplot_build(p3))
maxWidth = unit.pmax(pA$widths[2:3], pB$widths[2:3], 
                     pC$widths[2:3])

# Set the widths
pA$widths[2:3] <- maxWidth
pB$widths[2:3] <- maxWidth
pC$widths[2:3] <- maxWidth

grid.arrange(pA, pB, pC, ncol = 1, heights = c(1.7, 1, 1))

@@

% correlations with tide before/after wtreg
<<cor_res, cache = F, echo = F, eval = T, results = 'asis'>>=
# ######
# # table of DO/metab correlations before after, detiding
# # note that tide in met_ls is daily average of hourly tidal change
# 
# # metab and inst flux data
# load('met_ls.RData')
# load('met_ls_inst.RData')
# 
# # go through each site for DO cors, use metab list for metab cors
# case_regs <- list.files(getwd(), '_wtreg.RData')
# cor_res <- adply(matrix(case_regs),
#   1, 
#   .fun = function(x){
#   
#     # load wtreg data
#     load(x)
#     nm <- gsub('.RData', '', x)
#     dat_in <- get(nm)
#       
#     # DO obs v tide
#     do_obs <- with(dat_in, 
#       cor.test(DO_obs, Tide)
#       )
#     
#     # DO dtd v tide
#     do_dtd <- with(dat_in, 
#       cor.test(DO_dtd, Tide)
#       )
#     
#     # inst flux data
#     flux_in <- met_ls_inst[[x]]
#     
#     # DOF with dtide
#     flux_obs <- with(flux_in, 
#       cor.test(DOF_obs, dTide)
#       )
#     
#     # DOF_dtd with dtide
#     flux_dtd <- with(flux_in, 
#       cor.test(DOF_dtd, dTide)
#       )
#     
#     # get metab data from list
#     dat_in <- met_ls[[x]]
#     
#     # melt for quicker analysis
#     dat_in <- melt(dat_in, 
#       measure.var = c('Pg', 'Rt', 'NEM', 'Pg_dtd', 'Rt_dtd', 'NEM_dtd'), 
#       id.var = c('Tide'))
#     
#     met_cor <- dlply(dat_in, 
#       .(variable), 
#       function(y) cor.test(y$value, y$Tide)
#       )
#     names(met_cor) <- c('Pg_obs', 'Rt_obs', 'NEM_obs', 'Pg_dtd', 'Rt_dtd', 
#       'NEM_dtd')
#     
#     all_ls <- c(do_obs = list(do_obs), do_dtd = list(do_dtd),
#       flux_obs = list(flux_obs), flux_dtd = list(flux_dtd), met_cor)
#     
#     res_sum <- ldply(all_ls, 
#       function(x) with(x, c(estimate, p.value))
#       )
# 
#     res_sum
#     
#   })
# 
# cor_res$site <- factor(cor_res$X1, 
#   labels = gsub('_wtreg.RData', '', case_regs))
# cor_res$X1 <- NULL
# 
# names(cor_res) <- c('var', 'corr', 'pval', 'site')
# 
# cor_res$sub_var <- gsub('[A-Z,a-z]*_', '', cor_res$var)
# cor_res$var <- gsub('_obs|_dtd', '', cor_res$var)
# 
# save(cor_res, file = 'cor_res.RData')

@@

# subset all results for plotting
to_tab <- cor_res

to_tab <- dcast(cor_res, site + sub_var ~ var, value.var = 'corr')

@@

cap.val<-'Correlations of tidal changes at each site with continuous \\ac{DO} observations, instantaneous \\ac{DO} flux, and metabolism estimates (gross production, respiration, and net metabolism) before (observed) and after detiding with weighted regression.  \\ac{DO} values are correlated with predicated tidal height at each observation, \\ac{DO} flux values are correlated with tidal change between observations, and daily integrated metabolism estimates are correlated with daily tidal range.'

@@

% case study metabolism results, including perc anom
<<case_res, cache = F, echo = F, eval = T, results = 'asis'>>=
# metab and inst flux data
# load('met_ls.RData')
# 
# met_comp <- ldply(met_ls, function(x){
#   
#   # detided
#   anoms <- anoms.fun(x, pgvar = 'Pg_dtd', rtvar = 'Rt_dtd')
#   anoms <- data.frame(variable = 'Anom', anoms)
#   anoms <- melt(anoms, id.var = 'variable', variable.name = 'X1')[, c(2, 1, 3)]
#   subs <- na.omit(x[, c('Pg_dtd', 'Rt_dtd', 'NEM_dtd')])  
#   sums <- adply(t(subs),
#     1, 
#     function(y) data.frame(Avg = mean(y), se = sd(y)/sqrt(length(y)))
#     )
#   sums <- melt(sums, id.var = 'X1')
#   dtd <- rbind(anoms, sums)
#   dtd$X1 <- gsub('_dtd', '', dtd$X1)
#   dtd$Input <- 'Detided'
#   
#   # observed
#   anoms <- anoms.fun(x, pgvar = 'Pg', rtvar = 'Rt')
#   anoms <- data.frame(variable = 'Anom', anoms)
#   anoms <- melt(anoms, id.var = 'variable', variable.name = 'X1')[, c(2, 1, 3)]
#   subs <- na.omit(x[, c('Pg', 'Rt', 'NEM')])  
#   sums <- adply(t(subs),
#     1, 
#     function(y) data.frame(Avg = mean(y), se = sd(y)/sqrt(length(y)))
#     )
#   sums <- melt(sums, id.var = 'X1')
#   obs <- rbind(anoms, sums)
#   obs$Input <- 'Observed'  
#   
#   # output
#   out <- rbind(dtd, obs)
#   names(out) <- c('Metab', 'Metric', 'Value', 'Input')
#   
#   return(out)
#   
#   })
# 
# save(met_comp, file = 'met_comp.RData')

@@

@@

tab <- form_fun(to_tab[, -c(1:2)])
rows <- to_tab[, 2]
cap.val<-'Metabolism estimates (gross production, respiration, and net metabolism) for case studies using \\ac{DO} time series before (observed) and after (detided) application of weighted regression.  Means and standard errors are based on daily integrated metabolism estimates.  Anomalous values are the proportion of metabolism estimates that were negative for gross production and positive for respiration.'

foot.val<-'\\textsuperscript{\\textit{a}}Pg: gross production, Rt: respiration, NEM: net ecosystem metabolism' 
latex( 
  tab,
  file = '',
  rowlabel = 'Site',
  insert.bottom = foot.val,
  caption = cap.val,
  caption.loc = 'top',
  rgroup = gsub('_wtreg.RData', '', unique(to_tab$Site)),
  n.rgroup = rep(2, 4),
  cgroup = c('Pg\\textsuperscript{\\textit{a}}', 'Rt', 'NEM'),
  n.cgroup = c(3, 3, 2),
  rowname = rows,
  colheads=c(rep(c('Mean','Std. Err.', 'Anom'),2), c('Mean', 'Std. Err.')),
  label = 'tab:case_res'
  )
@

>>>>

% plots of summarized metabolism estimates, before/after detiding
\centering\vspace*{\fill}
<<metab_sum, cache = T, eval = F, echo = F, fig.cap = 'Test'>>=

# load metabolism data
load('met_ls.RData')

# subset metab estimates by 30 day window and tide prop 1
load('case_grds.RData')
sel_vec <- with(case_grds, which(Day == 30 & Tide == 1))

met_sub <- met_ls[grep(sel_vec, names(met_ls))]

# creat weekly, monthly, seasonal categories
met_sub <- llply(met_sub, 
  .fun = function(x){

    # add week, month cols
    x$week <- format(x$Date, '%W')
    x$month <- format(x$Date, '%m')

    # seas col
    x$seas <- car::recode(x$month, "c('01','02','03') = 'W'; 
      c('04','05','06') = 'Sp'; 
      c('07','08','09') = 'Su'; 
      c('10','11','12') = 'F'")

    x

  })

# aggregate by weekly, monthly, seasonal categories

@@

% correlations with tide before/after wtreg
<<cor_res, cache = F, echo = F, eval = T, results = 'asis'>>=
# ######
# # table of DO/metab correlations before after, detiding
# # note that tide in met_ls is daily average of hourly tidal change
# 
# # metab and inst flux data
# load('met_ls.RData')
# load('met_ls_inst.RData')
# load('case_grds.RData')
# 
# # go through each site for DO cors, use metab list for metab cors
# case_regs <- list.files(getwd(), '_wtreg_[0-9]*.RData')
# cor_res <- alply(matrix(case_regs),
#   1, 
#   .fun = function(x){
#   
#     # load wtreg data
#     load(x)
#     nm <- gsub('.RData', '', x)
#     dat_in <- get(nm)
#       
#     # DO obs v tide
#     do_obs <- with(dat_in, 
#       cor.test(DO_obs, Tide)
#       )
#     
#     # DO dtd v tide
#     do_dtd <- with(dat_in, 
#       cor.test(DO_dtd, Tide)
#       )
#     
#     # inst flux data
#     flux_in <- met_ls_inst[[x]]
#     
#     # DOF with dtide
#     flux_obs <- with(flux_in, 
#       cor.test(DOF_obs, dTide)
#       )
#     
#     # DOF_dtd with dtide
#     flux_dtd <- with(flux_in, 
#       cor.test(DOF_dtd, dTide)
#       ) 
#     
#     # get tidal range for metabolic day/night periods from flux_in
#     # for correlation with daily integrated metab
#     tide_rngs <- ddply(flux_in, 
#       .variables = c('met.date'),
#       .fun = function(x){
# #         sunrise <- suppressWarnings(diff(range(x[x$variable %in% 'sunrise', 'Tide'])))
# #         sunset <- suppressWarnings(diff(range(x[x$variable %in% 'sunset', 'Tide'])))
# #         if(sunrise == 'Inf') sunrise <- NA
# #         if(sunset == 'Inf') sunset <- NA
# #         daytot <- diff(range(x$Tide))
#         sunrise <- mean(diff(x[x$variable %in% 'sunrise', 'Tide'], na.rm = T))
#         sunset <- mean(diff(x[x$variable %in% 'sunset', 'Tide'], na.rm = T))
#         if(sunrise == 'Inf') sunrise <- NA
#         if(sunset == 'Inf') sunset <- NA
#         daytot <- mean(diff(x$Tide, na.rm = T))
#         
#         c(daytot, sunrise, sunset)
#         }
#       )
#     names(tide_rngs) <- c('Date','daytot', 'sunrise', 'sunset')
#     
#     # get metab data from list
#     dat_in <- met_ls[[x]]
#     dat_in <- merge(dat_in, tide_rngs, by = 'Date', all.x = T)
#     
#     # as list for all metab correlations
#     # Pg values correlated with tidal range during sunlight hours
#     # Rt values correlated with tidal range during night hours
#     # NEM values correlated with metabolic daily tidal range
#     met_cor <- list(
#       
#       Pg_obs = with(dat_in, 
#         cor.test(Pg, sunrise)
#         ),
#     
#       Rt_obs = with(dat_in, 
#         cor.test(Rt, sunset)
#         ),
#     
#       NEM_obs = with(dat_in, 
#         cor.test(NEM, daytot)
#         ),
#     
#       Pg_dtd = with(dat_in, 
#         cor.test(Pg_dtd, sunrise)
#         ),
#     
#       Rt_dtd = with(dat_in, 
#         cor.test(Rt_dtd, sunset)
#         ),
#     
#       NEM_dtd = with(dat_in, 
#         cor.test(NEM_dtd, daytot)
#         )
#       
#       )
#     
#     # DO and metab corrs combined
#     all_ls <- c(do_obs = list(do_obs), do_dtd = list(do_dtd),
#       flux_obs = list(flux_obs), flux_dtd = list(flux_dtd), met_cor)
#     
#     # convert the stats for each wtreg to data frame
#     res_sum <- ldply(all_ls, 
#       function(x) with(x, c(estimate, p.value))
#       )
#     names(res_sum) <- c('var', 'cor', 'pval')
# 
#     res_sum
#     
#   })
# names(cor_res) <- case_regs
# 
# # melt and make separate columns for site and window comb value
# cor_res <- melt(cor_res, id.var = names(cor_res[[1]]))  
# cor_res$site <- gsub('_wtreg_[0-9]*.RData', '', cor_res$L1)
# cor_res$wins <- as.numeric(gsub('^.*_wtreg_|.RData', '', cor_res$L1))
# 
# # merge with case_grds
# case_grds$wins <- as.numeric(row.names(case_grds))
# cor_res <- merge(cor_res, case_grds, by = 'wins', all.x = T)
# 
# # create columns for variable (DO, flux, etc.) and sub variable (obs, dtd)
# cor_res$sub_var <- gsub('^.*_', '', cor_res$var)
# cor_res$var <- gsub('_.*$', '', cor_res$var)
# 
# save(cor_res, file = 'cor_res.RData')
# 
# to_plo <- cor_res
# to_plo$group_var <- paste(to_plo$Tide, to_plo$sub_var)
# to_plo_obs <- to_plo[to_plo$sub_var %in% 'obs', ]
# p1 <- ggplot(to_plo[to_plo$sub_var %in% 'dtd',], 
#     aes(x = factor(Day), y = cor, colour = Tide, group = group_var)) +
#   geom_line() + 
#   geom_line(data = to_plo_obs, 
#     aes(x = factor(Day), y = cor, group = group_var), 
#     colour = 'black', size = 1) +
#   geom_point(aes(pch = sub_var)) +
#   facet_grid(var ~ site) +
#   ylim(c(-1, 1)) +
#   theme_bw()

@@

# subset cor_res for window of 30 days, tidal prop 1
cor_res <- cor_res[with(cor_res, Tide == 1 & Day == 30), ]

# make wide form
to_tab <- dcast(cor_res, site + sub_var ~ var, value.var = 'cor')

@@

cap.val<-'Correlations of tidal changes at each site with continuous \\ac{DO} observations, instantaneous \\ac{DO} flux, and metabolism estimates (gross production, respiration, and net metabolism) before (observed) and after detiding with weighted regression.  \\ac{DO} values are correlated with predicted tidal height at each observation, \\ac{DO} flux values are correlated with tidal change between observations, and metabolism estimates are correlated with mean tidal change between observations during day, night, or total, day periods for production, respiration, and net metabolism respectively.  Total day periods were defined as the approximate 24 hours between sunrises for two calendar days, where day was the time from sunrise to sunset and night was the following time from sunset to sunrise.  Results are for weighted regressions using a window of thirty days and tidal height proportion of one.'

@@

% case study metabolism results, including perc anom
<<case_res, cache = F, echo = F, eval = T, results = 'asis'>>=
# # metab estimates for each wtreg
# load('met_ls.RData')
# 
# # subset metab estimates by 30 day window and tide prop 1
# load('case_grds.RData')
# sel_vec <- with(case_grds, which(Day == 30 & Tide == 1))
# 
# met_sub <- met_ls[grep(sel_vec, names(met_ls))]
# 
# met_comp <- ldply(met_sub, function(x){
#   
#   # detided
#   anoms <- anoms.fun(x, pgvar = 'Pg_dtd', rtvar = 'Rt_dtd')
#   anoms <- data.frame(variable = 'Anom', anoms)
#   anoms <- melt(anoms, id.var = 'variable', variable.name = 'X1')[, c(2, 1, 3)]
#   subs <- na.omit(x[, c('Pg_dtd', 'Rt_dtd', 'NEM_dtd')])  
#   sums <- adply(t(subs),
#     1, 
#     function(y) data.frame(Avg = mean(y), se = sd(y)/sqrt(length(y)))
#     )
#   sums <- melt(sums, id.var = 'X1')
#   dtd <- rbind(anoms, sums)
#   dtd$X1 <- gsub('_dtd', '', dtd$X1)
#   dtd$Input <- 'Detided'
#   
#   # observed
#   anoms <- anoms.fun(x, pgvar = 'Pg', rtvar = 'Rt')
#   anoms <- data.frame(variable = 'Anom', anoms)
#   anoms <- melt(anoms, id.var = 'variable', variable.name = 'X1')[, c(2, 1, 3)]
#   subs <- na.omit(x[, c('Pg', 'Rt', 'NEM')])  
#   sums <- adply(t(subs),
#     1, 
#     function(y) data.frame(Avg = mean(y), se = sd(y)/sqrt(length(y)))
#     )
#   sums <- melt(sums, id.var = 'X1')
#   obs <- rbind(anoms, sums)
#   obs$Input <- 'Observed'  
#   
#   # output
#   out <- rbind(dtd, obs)
#   names(out) <- c('Metab', 'Metric', 'Value', 'Input')
#   
#   return(out)
#   
#   })
# 
# save(met_comp, file = 'met_comp.RData')

@@

# remove extra text on site variable
to_tab$Site <- gsub('_wtreg_[0-9]*.RData$', '', to_tab$Site)

@@

tab <- form_fun(to_tab[, -c(1:2)])
rows <- to_tab[, 2]
cap.val<-'Summary of metabolism estimates (gross production, respiration, and net metabolism) for case studies using \\ac{DO} time series before (observed) and after (detided) application of weighted regression.  Means and standard errors are based on daily integrated metabolism estimates.  Anomalous values are the proportion of metabolism estimates that were negative for gross production and positive for respiration.  Results are for weighted regressions with a window of thirty days and tidal height proportion of one.'

foot.val<-'\\textsuperscript{\\textit{a}}Pg: gross production, Rt: respiration, NEM: net ecosystem metabolism' 
latex( 
  tab,
  file = '',
  rowlabel = 'Site',
  insert.bottom = foot.val,
  caption = cap.val,
  caption.loc = 'top',
  rgroup = unique(to_tab$Site),
  n.rgroup = rep(2, 4),
  cgroup = c('Pg\\textsuperscript{\\textit{a}}', 'Rt', 'NEM'),
  n.cgroup = c(3, 3, 2),
  rowname = rows,
  colheads=c(rep(c('Mean','Std. Err.', 'Anom'),2), c('Mean', 'Std. Err.')),
  label = 'tab:case_res'
  )
@
